Increased productivity using Atomify - a real-time LAMMPS visualizer

### 2018-06-05 ms.tex
Some more fixes

\begin{figure}
	\centering
	\includegraphics[width=0.5\textwidth]{lj_flow/configuration.png}
	\caption{
		Initial configuration in our case study simulation.
		A periodic box consisting of $(40\times25\times25)$ FCC unit cells with reduced density $\rho^* = 0.8442$ where we will have gas flow in a cylinder with radius 10 (reduced length).
		The different colors indicate the regions of which different integration rules apply.
		\textcolor{atomify-blue}{Blue} atoms are fixed and do not move at all,
		whereas the \textcolor{atomify-yellow}{yellow} atoms are thermalized with a Langevin\citep{schneider1978molecular} dissipative thermostat to mimick the heat exchange with the frozen bulk atoms.
		The \textcolor{atomify-red}{red} and the \textcolor{atomify-green}{green} atoms are integrated normally, except the \textcolor{atomify-green}{green} gas atoms have an applied constant acceleration representing the pressure gradient.
		Setting up and verifying this system is simple using Atomify due to the real-time coloring of groups and regions.
    }
	\label{fig:cylinder_simulation}
\end{figure}

@@

\begin{itemize}  
	\item $r \leq 10$: applied pressure gradient
	\item $5 < r \leq 4$: regular time integration
	\item $9 < r \leq 12$: Dissipative Langevin thermostat
	\item $12 < r$: frozen.
\end{itemize}
The different radii are in reduced Lennard Jones units.

\subsection{Creating the initial geometry}
We create a new script in Atomify using \keys{\cmd+N}, and save it (\keys{\cmd+S}) as \code{run.in}.
Starting from the input script in listing \ref{lst:simple.in}, we modify it to create a larger simulation box with $(40\times25\times25)$ unit cells.
Remove the line \code{fix nve all nve} so atoms will stand still (we will add integrator later anyway).
We will modify this script to achieve what we described above, so we need to make sure that these commands happen \textit{before} the \code{run 1000} command in the script.
If not, LAMMPS will not execute them before we start visualizing.
To define the inner cylinder, we first specify the radius and the center before using the region command
\begin{lstlisting}[basicstyle=\tiny, frame = none, numbers=none, framexleftmargin=0pt, xleftmargin=-0.75cm, xrightmargin=0.0cm]
	variable R equal $(ly*0.25)
	variable c equal $(ly*0.5)
	region cylinder1 cylinder x $c $c $R EDGE EDGE
\end{lstlisting}
The region command will create a cylinder in the $x$-direction, with $(y,z)$-coordinates at the system center \code{\$c} with radius \code{\$R} using the full length of the cylinder specified when using \code{EDGE}.
We now press \keys{\cmd+R} to run the simulation to see how it looks.
As shown in Fig. \ref{fig:rightbar}, we can hover the specified region to highlight the atoms in that region.
When we hover the region, we immediately see that the cylinder is in fact not placed at the center of the system, as shown in Fig. \ref{fig:initial_configuration}a.
The reason is that LAMMPS operate with two different units, either the length unit or the lattice length unit. This is explained in the documentation, but is a common mistake.
To discover mistakes like this is quickly done with Atomify.
Since we have used \code{\$(0.5*lx)}, we need to specify \code{units box} in the region command, rerun the simulation with \keys{\cmd+R} which gives the desired result in figure  \ref{fig:initial_configuration}b.

>>>>

\begin{figure}
	\centering
	\includegraphics[width=0.5\textwidth]{lj_flow/configuration.png}
	\caption{
		Initial configuration in our case study simulation.
		A periodic box consisting of $(40\times25\times25)$ FCC unit cells with reduced density $\rho^* = 0.8442$ where we will have gas flow in a cylinder with radius 10 (reduced length).
		The different colors indicate the regions of which different integration rules apply.
		\textcolor{atomify-blue}{Blue} atoms are fixed and do not move at all,
		whereas the \textcolor{atomify-yellow}{yellow} atoms are thermalized with a Langevin\citep{schneider1978molecular} dissipative thermostat to mimick the heat exchange with the frozen bulk atoms.
		The \textcolor{atomify-red}{red} and the \textcolor{atomify-green}{green} atoms are integrated normally, except the \textcolor{atomify-green}{green} gas atoms have an applied constant acceleration representing the pressure gradient.
		Setting up and verifying the system is simple using Atomify due to i.e. the real-time coloring of groups and regions.
    }
	\label{fig:cylinder_simulation}
\end{figure}

@@

\begin{itemize}  
	\item $r \leq 10$: applied pressure gradient
	\item $r \leq 17$: regular time integration
	\item $14 < r \leq 17$: Dissipative Langevin thermostat
	\item $17 < r$: frozen.
\end{itemize}
The different radii are in reduced Lennard Jones units.

\subsection{Creating the initial geometry}
We create a new script in Atomify using \keys{\cmd+N}, and save it (\keys{\cmd+S}) as \code{run.in}.
Starting from the input script in listing \ref{lst:simple.in}, we modify it to create a larger simulation box with $(40\times25\times25)$ unit cells.
Remove the line \code{fix nve all nve} so atoms will stand still (we will add integrator later).
We will modify this script to achieve what we described above. To make sure LAMMPS executes our modifiction before visualization is started, we need to make sure that these commands happen \textit{before} the \code{run 1000} command.
If we don't, LAMMPS will run 1000 timesteps before our modifications.

To define the inner cylinder, we first specify the radius and the center before using the region command
\begin{lstlisting}[basicstyle=\tiny, frame = none, numbers=none, framexleftmargin=0pt, xleftmargin=-0.75cm, xrightmargin=0.0cm]
	variable R equal $(ly*0.25)
	variable c equal $(ly*0.5)
	region cylinder1 cylinder x $c $c $R EDGE EDGE
\end{lstlisting}
The region command will create a cylinder in the $x$-direction, with $(y,z)$-coordinates at the system center \code{\$c} with radius \code{\$R} using the full length of the cylinder specified when using \code{EDGE}.
We now press \keys{\cmd+R} to run the simulation to see how it looks.
As shown in Fig. \ref{fig:rightbar}, we can hover the specified region to highlight the atoms in that region.
When we hover the region, we immediately see that the cylinder is in fact not placed at the center of the system, as shown in Fig. \ref{fig:initial_configuration}a.
The reason is that LAMMPS operate with two different units, either the length unit or the lattice length unit. This is explained in the documentation, but is a common mistake.
To discover mistakes like this is quickly done with Atomify.
Since we have used \code{\$(0.5*lx)}, we need to specify \code{units box} in the region command, rerun the simulation with \keys{\cmd+R} which gives the desired result in figure  \ref{fig:initial_configuration}b.
